NURM: a tool to locate numerical differences in pipelines

### 2019-10-02 paper.tex
Edited the text of the experiment section

\begin{figure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \includegraphics[width=1\columnwidth]{images/fig1-a}
    \caption{Identification of temporary and multi-write files.
    (\href{https://docs.google.com/drawings/d/1rsbFwPjNPNMRhXUl4RSK3G0OaiJC7K-buiHN0hPD8eQ/edit?usp=sharing}{Source})}
    \label{fig:overview-capturing}
  \end{subfigure}
   \begin{subfigure}{\columnwidth}
    \centering
     \includegraphics[width=1\columnwidth]{images/fig1-b}
     \caption{Labelling process graphs including intermediary files.
     (\href{https://docs.google.com/drawings/d/1yblYuKWAD18aJe5JxBu2h1EysyoQA3YrsQj-1T3s0l8/edit?usp=sharing}{Source})}
     \label{fig:overview-labelling}
   \end{subfigure}
   \caption{An overview of NURM tool in two steps. First capturing intermediary files (a); then
            labelling process graphs (b).}
   \label{fig:overview}
  \end{figure}

@@

Since all the result files are captured in Condition 1, the tool 
is ready to label the piepeline processes based on the results in Condition 2.
However, another challenge is to label undetermined processes that read files with 
differences and write files with differences too. In this
situation, it is not possible to determine from the pipeline results 
whether the process created differences or 
was transparent.
To address this issue, we set hooks in the pipeline 
in Condition 2. Hooks are set by replacing the pipeline 
processes with a custom script. This custom script labels each process 
as \emph{transparent} or \emph{create differences} immediately after running 
the original executable. 
The replacement is done through the PATH variable, as before. Moreover, 
this custom script copies the results obtained from the same process in 
Condition 1 to the pipeline output in Condition 2 if 
it is invoked with the arguments of a process that created differences 
(Figure~\ref{fig:overview-labelling} - (3)). 
Differences are identified by comparing checksum of the output files for 
the same process in both conditions (Figure~\ref{fig:overview-labelling} - (2)).
We developed an incremental approach that consists of the following steps:

@@

The variety of computing infrastructures, particularly the operating system, is 
known to influence the reproducibility of computational pipelines because of the
creation of small numerical differences. 
These differences mainly correspond to the mathematical functions implemented 
in different operating system libraries.
For instance, changing the mathematical functions like \emph{expf()} and 
\emph{cosf()} which manipulate the precision of floating-point representations, 
between \emph{glibc} libraries in different operating systems can produce 
small numerical differences.
Besides, a similar issue is expected for any operating system which is 
based on \emph{glibc}, the GNU C library.

Indeed, the propagation and amplification of these tiny perturbations by analysis 
may cause a significant reproducibility issue. We focus on the differences 
created by different version of operating systems in computational pipelines. 
In particular, NURM-tool is tested on the neuroimaging applications which are 
predominantly using mathematical libraries.

@@

We used our tool to evaluate the effect of the operating system on results 
produced by the pipelines from the Human Connectome Project (\href{https://www.humanconnectome.org}{HCP}).
The HCP initiative is a significant effort that will acquire and analyze 
brain connectivity data from 1200 healthy adults.
It enables the neuroscience 
research community to discover relationships between brain circuits and 
individual behaviors. This helps to understand a wide range of brain disorders.
The HCP project provides (1) database services (ConnectomeDB) for storing and 
sharing primary and processed data freely, and (2) data analysis pipelines that 
are available under an open source license.

The HCP developed a set of pre-processing pipelines to process structural,
functional and diffusion MRI data acquired in the project. We focus on HCP
pre-processing pipelines for structural data, particularly PreFreeSurfer
and FreeSurfer.

According to~\cite{glasser2013}, main sub-pipelines of the HCP PreFreeSurfer are:
(1) Distortion Correction (DC) 
to correct the geometric distortions for routine MRI scans 
and produce an undistorted native structural volume space for each subject,
(2) Anatomical Average (AAve) to average same modality images (if more than one is available),
(3) ACPC (Anterior Commissure, Posterior Commissure) Alignment (ACPC-A) 
is aligning images to the MNI space to have the same orientation as 
the reference template,
(4) Brain Extraction (BExt) includes a robust initial brain extraction, using FSL's linear (FLIRT) 
and non-linear (FNIRT) registration, 
(5) Bias Field Correction (BFC) applies intensity inhomogenity correction on the registered images, 
%Calculates bias field using square root of the product of T1w and T2w images. 
(6) Atlas-Registration (AR) to register the subject's native structural volume space to MNI space as the last step.

Also, the main goals of HCP FreeSurfer pipeline are:
(1) improve the robustness of brain extraction,
(2) fine tune image registration,
(3) accurately place the surface images with high resolution data,
(4) perform FreeSurfer's standard folding-based surface registration 
to their surface atlas.

A detailed description of the analyses done in these
pipelines is available in~\cite{glasser2013}.

HCP data consists of brain images collected from an individual healthy person, 
in the age range between 22-35 years~\cite{van2013wu}. Data from 1200 subjects 
is available in \href{https://db.humanconnectome.org}{the ConnectomDB repository}. 
Such a directory containing the HCP data is denoted by the term ``subject".
In this paper, we randomly selected 20 unprocessed subjects from 
the HCP data release S500. All the subjects were scanned using the 3-tesla 
type of MRI scanners.

@@

The data were processed in the order PreFreeSurfer and FreeSurfer. 
Unprocessed subject data used as the input data for PreFreeSurfer and its output 
results used as the input data for FreeSurfer analysis in each operating system separately.
Through all the subjects, first, two runs were made on the same operating systems 
to be sure that identified differences are not coming from the operations with randomness.
Then we identified the processes in the pipelines that are responsible for 
the creation of differences using the NURM-tool.

It should be noted that some files may have the same data but 
different metadata in headers, including creation time, modification time and date, 
which turns to non-identical checksums. 
So, we added some other functions for the file comparison to be sure that differences 
are in part of the file data. 
Depending on the file type, we used functions from FreeSurfer software package to determine 
whether two files differ, including  
\emph{mri\_diff}, \emph{mris\_diff}, and \emph{lta\_diff} for comparing volumes, surface-based files, 
and lta files (transforms) respectively. 
These functions check data based on the volume dimentions, 
resolutions, pixel intensities,  
the number of surface vertices and neighbors, and geometry information. 
It then returns files differ if there be differences in any of these parameters.
Also, text files are compared using a custom function that compares the content line by line.

@@

Two types of differences can occur in the subjects due to the 
differences in the operating systems. One is inter-OS differences caused by the 
operating system library updates and the other type, intra-OS differences 
occur as a result of the pseudo-random processes used in the 
pipelines.

In our experiments, we identified the processes that create differences due to 
intra-OS differences.  
For example, process \emph{mris\_curvature}
computes mean and Gaussian curvatures of a cortical surface using 
the random variable in FreeSurfer.
To avoid such randomness we 
initialized random number generators using a seed state in 
the command line in which pipeline script calls the program.
This ensures that results are the same from run to run.
Therefore, NURM-tool can identify the processes in the pipelines 
that create inter-OS differences.

\subsubsection{Inter-OS binary differences}

In a previous study~\cite{Scaria2017}, we showed that the HCP pre-processing 
pipelines~\cite{glasser2013} were 
sensitive to operating system variation.

Figure~\ref{fig:fnirt_result} shows differences in the files 
that are created as a part of ACPC-Alignment in PreFreeSurfer.
The square pixels in the brain in the checkerboard images show the differences between results in two OSes. 
The RMSE (root mean squared error) value of results is 0.029 and the dice coefficient is 0.125.
In the next subsection, it is shown that such misalignment is created due to 
non-linear registration in \emph{FNIRT} process in PreFreeSurfer pipeline.

Furthermore, Figure 
\ref{fig:tissue_class} illustrates the heatmap binarized differences 
of the brain tissue segmentation across OSes in FreeSurfer pipeline.
These differences are accumulated from 20 subject results.
So, the magnitude of differences is in the range of 1-20 as the total number of subjects.
The darker blue pixels show differences among less subjests and 
the brighter blue pixels are related to the differences among more subjects.

%The brighter spots show relevant pixels in the segmented image which are different among more subjects.
%The RMSE and the dice coefficient values of results are 0.009 and 0.991 respectively.
%Each color represents a different structure in the brain.

\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{images/segmentation.png} 
    \caption{Differences between FNIRT results of one subject from PreFreeSurfer 
    (checkerboard image \emph{T2w\_acpc\_to\_MNI\_nonli.nii.gz}) (CentOS6 vs. 
    CentOS7). Right images show the zoomed version part of the images marked 
    by the red rectangle.} 
    \label{fig:fnirt_result}
\end{figure}

\subsubsection{PreFreeSurfer pipeline analysis}

First, subjects are clustered into different groups using the clustering method as described before.
We set the threshold value to zero for the clustering method. 
This turns to have the subjects with the same topology in each cluster.
Also, we used the nearest neighbor algorithm to calculate the distance between clusters.
Table~\ref{table:data-clusters} shows the PreFreeSurfer result of subject clustering. 
Among our dataset, we identified 4 types of subjects with 
different topology of \emph{process trees}. 
Differences correspond to the data processing that leads to producing disparate output file(s).
For example, subject type 3 missed output file \emph{T1w2\_gdc.nii.gz} after processing 
in comparison with subject type 1.
Besides, we verified that 
the \emph{process trees} were identical for all subjects of the same type in 
different versions of CentOS.

@@

Then, we determined the frequency of the processes that create differences in 
the pipeline in Figure~\ref{fig:pfs_freq}. \emph{FLIRT} is the most frequent 
process that produces differences.
Furthermore, the percentage of processes that introduce differences 
along with the 
sub-pipelines are depicted in this figure 
including linear registration with “\emph{FLIRT}” (in 
ACPC-Alignment, Brain Extraction, Distortion Correction, 
Atlas Registration), non-linear registration with “\emph{FNIRT}” (in 
Brain Extraction and Altas Registration), image warping with 
“\emph{new\_invwarp}” (in Brain Extraction and Atlas Registration). 
Also, differences were observed in image mean and standard-deviation 
computations in image interpolation with “\emph{fslmaths}” (in Anatomical Average). 
It can be seen that \emph{fslmaths} and \emph{FLIRT} 
are the processes that at least have one subprocess to produce differences across all the subjects.

@@

\subsubsection{FreeSurfer pipeline analysis}

We executed FreeSurfer pipeline on both OSes using a fixed input data, result of PreFreeSurfer on Centos 6, 
to determine the creation of differences. 
NURM tool identidied \emph{mris\_make\_surfaces} as the only process in the pipeline that create differences.
This process generates surface files for cortical and white matter surfaces, curvature file for cortical thickness and 
surface file estimate for layer IV of cortical sheet. 
In this analysis, the number of process that create differences are dropped becasue of 
using the static builds of FreeSurfer in which libaries are embeded in the pipeline package.

However, we found that inter-OS differences occur when pre-processed data are different in FreeSurfer. 
Using the result data from PreFreeSurfer, we executed FreeSurfer pipeline in each operating system separately.
FreeSurfer pipeline is unstable as it propagates and amplifies differences 
through the pipeline analysis.
Figure~\ref{fig:tissue_class} shows inter-OS differences  
as a result of propagation and amplification of differences. % that coming from PreFreeSurfer outputs.

@@

We indentified 4 processes that create differences 
among all 28 distinct processes that are involved in the PreFreeSurfer execution. 
The numerical instability in the 
PreFreeSurfer HCP pipeline arises mainly from linear 
registration processes implemented in FSL \emph{FLIRT}. 
We can see that \emph{FLIRT} creates differences in almost all the sub-pipelines. 
Therefore, it is important to more investigate about the registration procedure and find 
a way to stabilize this process.

In the second experiment, 
the analysis results obtained by the pipeline show that inter-OS differences are visually substabtial.
We see that statically builds of the pipeline improves reproducibility, but 
it would not improve the numerical stability of the pipeline. 
FreeSurfer pipeline propagates and amplifies the numerical differences that are created by the 
differences in the underlying operating system libraries.

In addition to variations of the operating system, there are other factors that may affect 
the results such as software versions, compilers, hardwares, etc.
Generally, we can use the Monte Carlo Arithmatic (MCA) to determine the numerical instability of the pipelines.
This argorithm perturbs every floating-point operation 
in the analysis based on the random rounding in each run. 
By this algorithm, NURM tool can easily locates which parts of the analysed source code are to be responsible 
for floating-point related instabilities.

Although we could identify the processes in the pipeline that create differeces, the functions 
that amplify these differences should be quantified in the future works.
For this purpose, we can evaluate the final result after perturbing the identified processes in the pipeline iterratively.
As a result, the processes that amplify differences would have a significant effect on the results independently.

@@

Our technique is able to characterize the stability of a pipeline
automatically. We identified the main causes of the inter-OS differences as (1) the evolution 
of the math libraries over the time and, (2) the instability of the pipelines. 
There are two ways to tackle this problem. The easy but less preferred solution is masking the instabilities.
This can be done by using, (1) single operating system for the processing of subjects, 
(2) containerizing the pipelines so that the 
processing is done on a more controlled environment, 
(3) increasing the numerical precision of the arithmetics, 
(4) building static executables by removing the host operating system library dependencies. 
These solutions only makes the problem invisible but the instability still remains.

>>>>

\begin{figure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \includegraphics[width=1\columnwidth]{images/fig1-a}
    \caption{Identification of temporary and multi-write files.
    (\href{https://docs.google.com/drawings/d/1rsbFwPjNPNMRhXUl4RSK3G0OaiJC7K-buiHN0hPD8eQ/edit?usp=sharing}{Source})}
    \label{fig:overview-capturing}
  \end{subfigure}
   \begin{subfigure}{\columnwidth}
    \centering
     \includegraphics[width=1\columnwidth]{images/fig1-b}
     \caption{Labelling process graphs including intermediary files.
     (\href{https://docs.google.com/drawings/d/1yblYuKWAD18aJe5JxBu2h1EysyoQA3YrsQj-1T3s0l8/edit?usp=sharing}{Source})}
     \label{fig:overview-labelling}
   \end{subfigure}
   \caption{An overview of NURM-tool in two steps. First capturing intermediary files (a); then
            labelling process graphs (b).}
   \label{fig:overview}
  \end{figure}

@@

Since all the result files are captured in Condition 1, the tool 
is ready to label the piepeline processes based on the results in Condition 2.
However, another challenge is to label undetermined processes that read files with 
differences and write files with differences too. In this
situation, it is not possible to determine from the pipeline results 
whether the process created differences or 
was transparent.
To address this issue, we set hooks in the pipeline 
in Condition 2. Hooks are set by replacing the pipeline 
processes with a custom script. This custom script labels each process 
as \emph{transparent} or \emph{create differences} immediately after running 
the original executable. 
The replacement is done through the PATH variable, as before. Moreover, 
this custom script copies the results obtained from the same process in 
Condition 1 to the pipeline output in Condition 2 if 
it is invoked with the arguments of a process that created differences 
(Figure~\ref{fig:overview-labelling} - (3)).

Differences are identified by comparing checksum of the output files for 
the same process in both conditions (Figure~\ref{fig:overview-labelling} - (2)).
In addition, the distance functions that are specific to file types can be added 
to our tool to ensure that differences belong to the file data part.
We developed an incremental approach that consists of the following steps:

@@

In this experiment, we analyse the numerical reproducibility of the computational pipelines 
and identify the origin of differences across the operating systems. 
Two types of differences can occur in the subjects due to the differences
in the operating systems. One is between-OS differences caused by the
operating system library updates and the other type, within-OS differences
occur as a result of the pseudo-random processes used in the pipelines.

In particular, NURM-tool is tested on the neuroimaging applications which are 
predominantly using mathematical libraries. Therefore, we expect to find 
differences as a result of changing the mathematical functions between operating system libraries.

This section describes datasets and pipelines used for the analyses, 
how data processed through the pipelines, and the results.

@@

We used our tool to evaluate the reproducibility of the pipelines from the Human Connectome 
Project (\href{https://www.humanconnectome.org}{HCP}).
The HCP initiative is a significant effort to acquire and analyze 
brain connectivity data from 1200 healthy adults.
It enables the neuroscience 
research community to discover relationships between brain circuits and 
individual behaviors. This helps to understand a wide range of brain disorders.
The HCP project provides (1) database services (ConnectomeDB) for storing and 
sharing primary and processed data freely, and (2) data analysis pipelines that 
are available under an open-source license.

The HCP developed a set of pre-processing pipelines to process structural,
functional, and diffusion MRI data acquired in the project. We focus on HCP
pre-processing pipelines for structural data, particularly PreFreeSurfer
and FreeSurfer.

According to~\cite{glasser2013}, the sequence of the 
sub-pipelines in PreFreeSurfer includes 
(1) Distortion Correction (DC), 
(2) Anatomical Average (AAve), 
(3) ACPC (Anterior Commissure, Posterior Commissure) Alignment (ACPC-A), 
(4) Brain Extraction (BExt), 
(5) Bias Field Correction (BFC), 
(6) Atlas-Registration (AR).

Also, the sequence of the main sub-pipelines in FreeSurfer includes 
(1) Downsampling images, 
(2) T1w image registration, 
(3) Placement of surface images, 
(4) Folding-based surface registration.
A detailed description of the analyses done in these
pipelines is available in~\cite{glasser2013}.

Furthermore, the average time per subject taken for PreFreeSurfer processing is 2.2 hours, 
and FreeSurfer processing is 8.3 hours (20 runs), 
and the average output file size of PreFreeSurfer processing is 2.7 GB, 
and FreeSurfer processing is 4.1 GB (20 subjects).

HCP data collected from different types of imaging techniques, including 
structural imaging (sMRI), functional imaging (fMRI), and diffusion imaging (dMRI).
The structural images include T1-weighted (T1w) and T2-weighted (T2w) images which 
help in the diagnosis of the brain injury.
The functional images, including task-based fMRI and resting-state scans, 
enable the measurement of functional activations within brain areas. 
Diffusion imaging is another kind of MRI technique, which measures 
the anatomical connectivity between regions.
See~\cite{van2013wu} for a discussion of these various terms.

Data from 1200 subjects 
is available in \href{https://db.humanconnectome.org}{the ConnectomDB repository}. 
In this paper, we randomly selected 20 unprocessed subjects from 
the HCP data release S500. All the subjects were scanned using the 3-tesla 
type of MRI scanners.

@@

The data were processed with PreFreeSurfer and FreeSurfer. 
First, PreFreeSurfer was utilized to analyse the unprocessed data, and then its 
results were used as the input of FreeSurfer.

Each subject was processed twice on the same operating system to detect
variability coming from pseudo-random operations. 
Within-OS variability may also be coming from other factors than pseudo-randomness. 
For instance, metadata may differ due to the presence of timestamps, 
file paths, and other execution-specific information. 
To ensure that differences belong to the file data part, 
we added distance functions specific to the file types.
These functions are \emph{mri\_diff}, \emph{mris\_diff}, and \emph{lta\_diff} 
for comparing volumes, surface-based files, 
and lta files (transforms) respectively. 
These functions compare files based on the image dimensions, 
pixel intensities, the number of vertices, and geometry information
(see~\cite{fischl2012freesurfer} for more details).

Furthermore, we clustered subjects into different type using 
the clustering method as described before.
We set the threshold value to zero for the clustering method. 
This turns to cluster the subjects with the same topology into the same type.
Also, we used the nearest neighbor algorithm to calculate the distance between clusters.

@@

\subsubsection{Within-OS differences}

In our experiments, we identified two processes that create differences due to 
within-OS differences.  
Registration process with \emph{mri\_segreg} and process \emph{mris\_curvature} that 
computes mean and Gaussian curvatures of a cortical surface using 
the random variable in FreeSurfer.
To avoid such pseudo-randomness, we 
initialized random number generators using a seed state in 
the command line in which pipeline script calls the process.
In this way, NURM-tool identifies the processes in the pipelines 
that create between-OS differences.

\subsubsection{Between-OS differences in PreFreeSurfer}
%\subsubsection{PreFreeSurfer pipeline analysis}

Table~\ref{table:data-clusters} shows the PreFreeSurfer result of subject clustering. 
Among our dataset, we identified four types of subjects with 
the different topology of \emph{process trees}. 
Differences correspond to the data processing that leads to producing a disparate output file(s).
For example, subject type 3 missed output file \emph{T1w2\_gdc.nii.gz} after processing 
in comparison with subject type 1.
Besides, we verified that 
the \emph{process trees} were identical for all subjects of the same type in 
different versions of CentOS.

@@

The frequency of the processes that create differences in 
the pipeline among 20 subjects is determined in Figure~\ref{fig:pfs_freq}. 
\emph{FLIRT} is the most frequent process that produces differences.
Furthermore, the percentage of processes that introduce differences 
along with the 
sub-pipelines are depicted in this figure 
including linear registration with “\emph{FLIRT}” (in 
ACPC-Alignment, Brain Extraction, Distortion Correction, 
Atlas Registration), non-linear registration with “\emph{FNIRT}” (in 
Brain Extraction and Altas Registration), image warping with 
“\emph{new\_invwarp}” (in Brain Extraction and Atlas Registration). 
Besides, differences were observed in image mean and standard-deviation 
computations in image interpolation with “\emph{fslmaths}” (in Anatomical Average). 
Results show that \emph{fslmaths} and \emph{FLIRT} 
are the processes that at least have one subprocess to produce differences across all the subjects.

@@

We created checkerboard images from the image results of one subject in two OSes.
Alternating rectangular regions between two images, creating a characteristic 
checkerboard-like pattern of varying magnitudes.
Figure~\ref{fig:fnirt_result} shows differences in the files 
that are created as a part of ACPC-Alignment in PreFreeSurfer.
Each rectangle includes the pixels with different intensity values between images.

\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{images/segmentation.png} 
    \caption{Differences between FNIRT results of one subject from PreFreeSurfer 
    (checkerboard image \emph{T2w\_acpc\_to\_MNI\_nonli.nii.gz}) (CentOS6 vs. 
    CentOS7). Right images show the zoomed version part of the images marked 
    by the red rectangle.
    Here is 
    \href{https://raw.githubusercontent.com/ali4006/HCP-reproducibility-paper/master/images/brain_classification.gif}{the link}
    to the gif animation of the same images.
} 
    \label{fig:fnirt_result}
\end{figure}

\subsubsection{Between-OS differences in FreeSurfer}

In the first test, the results of PreFreeSurfer on CentOS 6
feed to the FreeSurfer pipeline on both OSes.
We fixed input data to determine whether the pipeline creates differences.
We processed 20 subjects using FreeSurfer.
NURM-tool identified \emph{mris\_make\_surfaces} as the only process in 
the pipeline that creates differences in 10 subjects.
This process generates surface files for cortical and white matter surfaces (see~\cite{} for more details).
Also, FreeSurfer did not introduce any differences in 10 subjects.

Results show that the static builds of FreeSurfer in which uses the embedded libraries, 
significantly avoids the creation of differences.
However, we found that between-OS differences occur when pre-processed data are different in FreeSurfer.

In the second test, the results of PreFreeSurfer feed to the FreeSurfer 
pipeline on each operating system separately.
Figure~\ref{fig:tissue_class} shows between-OS differences  
as a result of propagation and amplification of differences in FreeSurfer. % that coming from PreFreeSurfer outputs. 
This figure illustrates the sum of binarized differences 
from 20 subject results of the brain tissue segmentation across OSes.
Therefore, the magnitude of differences is in the range of 1-20 as the total number of subjects.

@@

We identified four processes that create differences 
among all 28 distinct processes that are involved in the PreFreeSurfer execution. 
The numerical instability in the 
PreFreeSurfer HCP pipeline arises mainly from linear 
registration processes implemented in FSL \emph{FLIRT}. 
We can see that \emph{FLIRT} creates differences in almost all the sub-pipelines. 
Therefore, it is important to investigate the registration procedure and find 
a way to stabilize this process.

In the second experiment, 
the analysis results obtained by the pipeline show that between-OS differences are visually substantial.
We see that statically builds of the pipeline improves reproducibility, but 
it would not improve the numerical stability of the pipeline. 
FreeSurfer pipeline propagates and amplifies the numerical differences that are created by the 
differences in the underlying operating system libraries.

In addition to variations of the operating system, other factors exist which may influence 
the reproducibility of the analyses such as software versions, compilers, hardware, etc.
Generally, we can use the Monte Carlo Arithmetic (MCA) to determine the numerical stability of the pipelines.
This algorithm perturbs every floating-point operation 
in the analysis based on the random rounding in each run. 
By this algorithm, NURM-tool can easily locate which parts of the analyzed source code are responsible 
for the floating-point related instabilities.

Although we identify the processes in the pipeline that create differences, 
the amplification of these differences should be quantified in the future works.
For this purpose, we can evaluate the final result after perturbing the identified processes in the pipeline iteratively.
As a result, the processes that amplify differences would have a significant effect on the results.

@@

Our technique can characterize the stability of the pipelines
automatically. We identified the main causes of the between-OS differences as (1) the evolution 
of the math libraries over time and, (2) the instability of the pipelines. 
There are two ways to tackle this problem. The easy but less preferred solution is masking the instabilities.
This can be done by using, (1) single operating system for the processing of subjects, 
(2) containerizing the pipelines so that the 
processing is done on a more controlled environment, 
(3) increasing the numerical precision of the arithmetics, 
(4) building static executables by removing the host operating system library dependencies. 
These solutions only make the problem invisible, but the pipelines are stiil unstable.
